---
title: "GNET - 4E & diff judgements - basic analysis"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 4
---

# GNET - 4 elements with difference ratings from participants

This is the analysis of the second run of GNET4E.
Everything is the same, except that in the study phase participants looked at a familiar first then a novel and rated the subjective difference of the images.

As in the original task, stimuli were algorithmically generated, allowing precise comparison between stimuli.
The difference between the stimulus presented and other stimuli (several comparisons are used) is a proxy for novelty.

During familiarization, participants learned a set of 5 stimuli
During the study phase, they rated the difference of these stimuli to novels.
During the test phase, the performed a recognition memory test for the novels intermixed with distractors.
- Novels and distractors were balanced.

In the original GNET, recognition performance tended to increase monotonically with difference to familiars
In the GNET4E participants showed their highest categorization performance for stimuli at intermediate levels of difference.

## Difference indices

```{r preparations, include=FALSE}
source("01_DIFFERENCE_CALCULATIONS.R")

library(tidyverse)
library(ez)
library(emmeans)
library(DescTools)
library(afex)
library(effsize)
library(Hmisc)

gnet2_data <- read_csv(
  "gnet_v2_jd_data.csv",
  locale = locale(encoding = "UTF-8")
) %>%
  select(
    count_study_sequence,
    count_test_sequence,
    datetime,
    response,
    response_study_response,
    response_test_response,
    response_time,
    response_time_study_response,
    response_time_test_response,
    stim,
    stim_2,
    studyResultId,
    total_responses,
    workerId
  ) %>%
  filter(!is.na(workerId)) %>%
  mutate(
    stimtype = case_when(
      is.na(count_test_sequence) & str_detect(stim_2, "prototype") ~ "prototype",
      is.na(count_test_sequence) & str_detect(stim_2, "p[1-5]d1") ~ "D1",
      is.na(count_test_sequence) & str_detect(stim_2, "p[1-5]d2") ~ "D2",
      is.na(count_test_sequence) & str_detect(stim_2, "p[1-5]d3") ~ "D3",
      is.na(count_test_sequence) & str_detect(stim_2, "p[1-5]d4") ~ "D4",
      is.na(count_test_sequence) & str_detect(stim_2, "p[6-9]") ~ "D5",
      is.na(count_test_sequence) & str_detect(stim_2, "p10") ~ "D5",

      !is.na(count_test_sequence) & str_detect(stim, "p[1-5]d1") ~ "D1",
      !is.na(count_test_sequence) & str_detect(stim, "p[1-5]d2") ~ "D2",
      !is.na(count_test_sequence) & str_detect(stim, "p[1-5]d3") ~ "D3",
      !is.na(count_test_sequence) & str_detect(stim, "p[1-5]d4") ~ "D4",
      !is.na(count_test_sequence) & str_detect(stim, "p[6-9]") ~ "D5",
      !is.na(count_test_sequence) & str_detect(stim, "p10") ~ "D5",

      TRUE ~ NA_character_
    ),

    test_quality = case_when(
      str_detect(stim, "_[1-2]") & !is.na(response_time_test_response) ~ "fam",
      str_detect(stim, "_[3-4]") & !is.na(response_time_test_response) ~ "new",
      TRUE ~ NA_character_
    ),

    rt_corr = case_when(
      str_detect(stim, "_[1-2]") & response_test_response == "left"  ~ 1,
      str_detect(stim, "_[1-2]") & response_test_response == "right" ~ 0,
      str_detect(stim, "_[3-4]") & response_test_response == "left"  ~ 0,
      str_detect(stim, "_[3-4]") & response_test_response == "right" ~ 1,
      TRUE ~ NA_real_
    )
  )
```

```{r add_diff_indices, include=FALSE}
# preprocessed data and difference indices are used to calculate study and test indices

gnet2_data <- gnet2_data %>%
  rowwise() %>%
  mutate(
    match_row = which(str_detect(stim_2, fixed(difference_indices$stimulus_id)))[1],
    DTF = ifelse(is.na(match_row), 0, difference_indices$DTF[match_row]),
    DTAF = ifelse(is.na(match_row), 0, difference_indices$DTAF[match_row]),
    DTAN = ifelse(is.na(match_row), 0, difference_indices$DTAN[match_row]),
    DTN = ifelse(is.na(match_row), 0, difference_indices$DTN[match_row])
  ) %>%
  ungroup() %>%
  select(-match_row) %>%
  mutate(
    identifier = paste0(workerId, "_", studyResultId)
  )
```

```{r difference_ratings, include=FALSE}
# Calculate each participant's subjective difference ratings during the study phase.
# For every participant (workerId/studyResultId) and stimulus category (stimtype),
# compute both the mean and standard deviation of the difference judgments
# (response_study_response), then create a unique participant-session identifier.

# study DT ####
gnet2_data <- gnet2_data %>%
  mutate(
    response_study_response = na_if(response_study_response, "None"),
    response_study_response = as.numeric(response_study_response)
  )

mean_jds <- gnet2_data %>%
  filter(
    !is.na(response_study_response),
    is.na(count_test_sequence)
  ) %>%
  group_by(workerId, studyResultId, stimtype) %>%
  summarise(
    response_study_response = mean(response_study_response),
    .groups = "drop"
  )

sd_jds <- gnet2_data %>%
  filter(
    !is.na(response_study_response),
    is.na(count_test_sequence)
  ) %>%
  group_by(workerId, studyResultId, stimtype) %>%
  summarise(
    response_study_response = sd(response_study_response),
    .groups = "drop"
  )

mean_sd_jds <- mean_jds %>%
  rename(mean_jd = response_study_response) %>%
  left_join(
    sd_jds %>%
      rename(sd_jd = response_study_response),
    by = c("workerId", "studyResultId", "stimtype")
  )

mean_sd_jds <- mean_sd_jds %>%
  mutate(
    identifier = paste0(workerId, "_", studyResultId)
  )

rm(mean_jds,sd_jds)

#####
# mean_sd_jds is output - difference ratings mean and sd for each group of stim for each participant
```

```{r test_data, include=FALSE}
# Create a participant-level recognition memory contingency table.
# For each participant and stimulus type, count familiar hits, misses,
# novel correct rejections, false alarms, and missing responses.
# The resulting table contains one row per participant × stimulus type.

test_dat <- gnet2_data %>%
  filter(!is.na(count_test_sequence)) %>%
  count(
    studyResultId,
    workerId,
    stimtype,
    test_quality,
    rt_corr,
    name = "N"
  ) %>%
  mutate(
    identifier = paste0(workerId, "_", studyResultId)
  )

test_dat_c <- test_dat %>%
  complete(
    identifier,
    stimtype,
    test_quality,
    rt_corr,
    fill = list(N = 0)
  )

test_dat_compl <- test_dat_c %>%
  mutate(
    response_type = case_when(
      test_quality == "fam" & is.na(rt_corr) ~ "fam_NA",
      test_quality == "fam" & rt_corr == 1 ~ "fam_corr",
      test_quality == "fam" & rt_corr == 0 ~ "fam_miss",
      test_quality == "new" & is.na(rt_corr) ~ "new_NA",
      test_quality == "new" & rt_corr == 1 ~ "new_corr",
      test_quality == "new" & rt_corr == 0 ~ "new_fa"
    )
  ) %>%
  select(identifier, stimtype, response_type, N) %>%
  pivot_wider(
    names_from = response_type,
    values_from = N,
    values_fill = 0
  ) %>%
  separate(
    identifier,
    into = c("workerId", "studyResultId"),
    sep = "_",
    remove = FALSE
  ) %>%
  select(
    studyResultId,
    workerId,
    stimtype,
    identifier,
    fam_NA,
    fam_corr,
    fam_miss,
    new_NA,
    new_corr,
    new_fa
  )

rm(test_dat,test_dat_c)
#####
# test_dat_compl is output
```

```{r exclusions, include=FALSE}
# Exclusions -------------------------------------------------------------

# Runs with all 160 trials
usable <- gnet2_data %>%
  count(workerId, studyResultId, name = "N") %>%
  filter(N == 160) %>%
  arrange(studyResultId) %>%
  distinct(workerId, .keep_all = TRUE) %>%
  mutate(
    identifier = paste0(workerId, "_", studyResultId)
  )

fineids <- usable$identifier

# Number of missed study-phase responses
study_miss <- gnet2_data %>%
  filter(
    response == "None",
    is.na(count_test_sequence)
  ) %>%
  count(workerId, studyResultId, name = "N") %>%
  mutate(
    identifier = paste0(workerId, "_", studyResultId)
  )

# Exclude participants with too many missed study responses
stmisslimit <- 20

drop_ids_stmiss <- study_miss %>%
  filter(N >= stmisslimit) %>%
  pull(identifier)

dropbystmiss <- length(drop_ids_stmiss)

fineids <- setdiff(fineids, drop_ids_stmiss)

mean_sd_jds <- mean_sd_jds %>%
  filter(identifier %in% fineids)

test_dat_compl <- test_dat_compl %>%
  filter(identifier %in% fineids)

# Exclude participants with too many missed test responses
noresp <- test_dat_compl %>%
  mutate(total_NA = fam_NA + new_NA) %>%
  group_by(identifier) %>%
  summarise(
    total_NA = sum(total_NA),
    .groups = "drop"
  )

rtmisslimit <- 33

drop_ids_rtmiss <- noresp %>%
  filter(total_NA > rtmisslimit) %>%
  pull(identifier)

dropbyrtmiss <- length(drop_ids_rtmiss)

fineids <- setdiff(fineids, drop_ids_rtmiss)

mean_sd_jds <- mean_sd_jds %>%
  filter(identifier %in% fineids)

test_dat_compl <- test_dat_compl %>%
  filter(identifier %in% fineids)

# Exclude participants who judged prototype-prototype pairs as too different
protj <- mean_sd_jds %>%
  filter(stimtype == "prototype")

# this now doesnt exclude anyone!

drop_ids_misjud <- protj %>%
  filter(mean_jd > 15) %>%
  pull(identifier)

dropbymisjud <- length(drop_ids_misjud)

# filter data accordingly

fineids <- setdiff(fineids, drop_ids_misjud)

mean_sd_jds <- mean_sd_jds %>%
  filter(identifier %in% fineids)

test_dat_compl <- test_dat_compl %>%
  filter(identifier %in% fineids)

gnet2_data <- gnet2_data %>%
  filter(identifier %in% fineids)

```

# Exclusions

We excluded `r dropbystmiss` participants due to a high number of missed
responses in the study phase (≥ `r stmisslimit`).

We excluded `r dropbyrtmiss` participants due to a high number of missed
responses in the recognition test (> `r rtmisslimit`).

We excluded `r dropbymisjud` participants due to inattention to task
details, indicated by a mean difference judgment > 5 for prototype–
prototype comparisons.

This left `r n_distinct(mean_sd_jds$identifier)` participants in the
analysis.

The identifiers are:

`r paste(unique(mean_sd_jds$identifier), collapse = ", ")`

# Study phase

Participants make a judgement of the difference between a prototype and a novel picture.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

ggplot(mean_sd_jds,
       aes(x = stimtype, y = mean_jd, color = stimtype)) +
  geom_jitter(width = 0.2, alpha = 0.5) +
  stat_summary(
    geom = "errorbar",
    fun.data = mean_se,
    width = 0.2
  ) +
  stat_summary(
    geom = "point",
    fun = mean,
    color = "black",
    size = 2,
    shape = 16
  ) +
  stat_summary(
    fun = mean,
    geom = "text",
    color = "black",
    show.legend = FALSE,
    vjust = 5,
    aes(label = round(after_stat(y), 3))
  )

```

# Test phase

Test phase was the same as before: participants see the novel pictures from the study phase with distractors from the same categories. They signal if they think the picture is an old one from the study phase, or a novel distractor.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

print("Correct recognition for familiars in test")
ggplot(test_dat_compl, aes(x=stimtype, y=fam_corr))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("False alarm for novels in test")
ggplot(test_dat_compl, aes(x=stimtype, y=new_fa))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

test_dat_compl <- test_dat_compl %>%
  mutate(
    CorrectedRecognitions = fam_corr - new_fa,
    CorrectedRejections = new_corr - fam_miss,
    OCCategorizations = CorrectedRecognitions + CorrectedRejections
  )

print("ANOVA with correct recognition minus false alarm or miss by fam/nov")
a1 <- aov_ez("identifier", "CorrectedRecognitions",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=CorrectedRecognitions, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("ANOVA with correct rejection minus false alarm or miss by fam/nov")
a1 <- aov_ez("identifier", "CorrectedRejections",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=CorrectedRejections, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("ANOVA with corrected differentiation score by category ((crecog-fa)+(creject-fa))")
a1 <- aov_ez("identifier", "OCCategorizations",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=OCCategorizations, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

```

# Mixed models

```{r mixed_models, include=FALSE}
library(lme4)
library(lmerTest)
library(sjPlot)

lmmdat <- gnet2_data

stlmm <- lmmdat %>%
  filter(is.na(test_quality))

tdlmm <- lmmdat %>%
  filter(!is.na(test_quality))

tdlmm <- tdlmm %>%
  mutate(
    rt_resp = recode(
      response_test_response,
      "left" = 0,
      "right" = 1,
      .default = NA_real_
    ),
    stimtype = factor(stimtype),
    test_quality = factor(test_quality),
    rt_corr = as.numeric(rt_corr)
  )
```

## Mixed models

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

library(lme4)
library(sjPlot)

logmr <- glmer(
  rt_resp ~ stimtype * test_quality + (1 | workerId),
  data = tdlmm,
  family = binomial
)

summary(logmr)

plot_model(logmr, type = "int")

emmeans(logmr, pairwise ~ test_quality | stimtype)


logmr2 <- glmer(
  rt_resp ~ DTF * test_quality + (1 | workerId),
  data = tdlmm,
  family = binomial
)

summary(logmr2)

plot_model(logmr2, type = "int")


logmr3 <- glmer(
  rt_resp ~ DTAF * test_quality + (1 | workerId),
  data = tdlmm,
  family = binomial
)

summary(logmr3)

plot_model(logmr3, type = "int")


logmr4 <- glmer(
  rt_resp ~ DTAN * test_quality + (1 | workerId),
  data = tdlmm,
  family = binomial
)

summary(logmr4)

plot_model(logmr4, type = "int")


logmr5 <- glmer(
  rt_resp ~ DTN * test_quality + (1 | workerId),
  data = tdlmm,
  family = binomial
)

summary(logmr5)

plot_model(logmr5, type = "int")

tab_model(
  logmr,
  logmr2,
  logmr3,
  logmr4,
  logmr5,
  show.est = TRUE,
  show.se = TRUE,
  show.r2 = TRUE,
  show.aic = TRUE,
  show.aicc = TRUE,
  transform = NULL
)


```

## ALT - Mixed models

Use sum-to-zero contrasts so that coefficients are interpreted as
deviations from the grand mean rather than comparisons with the
reference level (D1). This is useful when no stimulus type serves
as a theoretically meaningful baseline condition.


```{r  eval = TRUE, warning=FALSE, echo=FALSE}
contrasts(tdlmm$stimtype) <- contr.sum
contrasts(tdlmm$test_quality) <- contr.sum

model <- glmer(
  rt_resp ~ stimtype * test_quality + (1 | workerId),
  data = tdlmm,
  family = binomial
)

summary(model)
```

## image effects

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
mod_img <- glmer(
  rt_resp ~ stimtype * test_quality +
    (1 | workerId) +
    (1 | stim),
  data = tdlmm,
  family = binomial
)
summary((mod_img))

emmeans(mod_img, pairwise ~ test_quality | stimtype)
```

## is the interaction significant?

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
mod_no_interaction <- glmer(
  rt_resp ~ stimtype + test_quality +
    (1 | workerId) + (1 | stim),
  data = tdlmm,
  family = binomial
)

anova(mod_no_interaction, mod_img)
```
