---
title: "Graded Novelty Enoding Task - 4 shapes version - judge difference"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
---
```{r  include=FALSE}
source("difference_innumbers.R")
source("gnet_v2_jd_processdata.R")

library(ez)
library(ggplot2)
library(emmeans)
library(DescTools)
library(stats)
library(afex)
library(effsize)
```

```{r  include=FALSE}
# preprocessed data and difference indices are used to calculate study and test indices
gnet2_data$DTF <- 0
gnet2_data$DTAF <- 0
gnet2_data$DTAN <- 0
gnet2_data$DTN_byPhase <- 0

for (i in 1:nrow(gnet2_data)){
  for (j in 1:nrow(difference_indices)){
    if (grepl(difference_indices$pict[j],gnet2_data$stim[i])){
      gnet2_data$DTF[i] <- difference_indices$DTF[j]
      gnet2_data$DTAF[i] <- difference_indices$DTAF[j]
      gnet2_data$DTAN[i] <- difference_indices$DTAN[j]
      gnet2_data$DTN_byPhase[i] <- difference_indices$DTN_byPhase[j]
    }
  }
}
# at this point we have all the data with all of the calculated difference indicators
gnet2_data$identifier <- paste(gnet2_data$workerId, "_", gnet2_data$studyResultId, sep="")
```

```{r  include=FALSE}
# study DT ####
gnet2_data[response_study_response == "None",
           response_study_response := NA]
gnet2_data$response_study_response <- as.numeric(gnet2_data$response_study_response)

mean_jds <- gnet2_data[!is.na(response_study_response) & is.na(count_test_sequence),
                       mean(response_study_response),by=c("workerId","studyResultId","stimtype")]
sd_jds <- gnet2_data[!is.na(response_study_response) & is.na(count_test_sequence),
                     sd(response_study_response),by=c("workerId","studyResultId","stimtype")]
mean_jds$identifier <- paste(mean_jds$workerId, "_", mean_jds$studyResultId, sep="")

#####
# mean_jds is output

# GENERATE TEST DT ####
test_dat <- gnet2_data[!is.na(count_test_sequence), .N, by=.(studyResultId,workerId,stimtype,test_quality,rt_corr)]

test_dat$identifier <- paste(test_dat$workerId, "_", test_dat$studyResultId, sep="")

mycols  = c("identifier","stimtype","test_quality","rt_corr")
setkeyv(test_dat,mycols)
test_dat_c <- test_dat[J(do.call(CJ,lapply(mycols,function(x)unique(get(x)))))]
for (i in 1:nrow(test_dat_c)){
  if (is.na(test_dat_c$N[i])){
    test_dat_c$N[i] <- 0
  }
}

fna <- test_dat_c[is.na(rt_corr) & test_quality == "fam",]
fna$workerId <- c(fna[,str_split(identifier, pattern = "_")][1])
fna$studyResultId <- c(fna[,str_split(identifier, pattern = "_")][2])
colnames(fna) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","fam_NA","identifier")
fc <- test_dat_c[rt_corr == 1 & test_quality == "fam",]
fc$workerId <- c(fc[,str_split(identifier, pattern = "_")][1])
fc$studyResultId <- c(fc[,str_split(identifier, pattern = "_")][2])
colnames(fc) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","fam_corr","identifier")
ff <- test_dat_c[rt_corr == 0 & test_quality == "fam",]
ff$workerId <- c(ff[,str_split(identifier, pattern = "_")][1])
ff$studyResultId <- c(ff[,str_split(identifier, pattern = "_")][2])
colnames(ff) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","fam_miss","identifier")

nna <- test_dat_c[is.na(rt_corr) & test_quality == "new",]
nna$workerId <- c(nna[,str_split(identifier, pattern = "_")][1])
nna$studyResultId <- c(nna[,str_split(identifier, pattern = "_")][2])
colnames(nna) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","new_NA","identifier")
nc <- test_dat_c[rt_corr == 1 & test_quality == "new",]
nc$workerId <- c(nc[,str_split(identifier, pattern = "_")][1])
nc$studyResultId <- c(nc[,str_split(identifier, pattern = "_")][2])
colnames(nc) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","new_corr","identifier")
nf <- test_dat_c[rt_corr == 0 & test_quality == "new",]
nf$workerId <- c(nf[,str_split(identifier, pattern = "_")][1])
nf$studyResultId <- c(nf[,str_split(identifier, pattern = "_")][2])
colnames(nf) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","new_fa","identifier")

fams <- merge(fna,fc,by=c("stimtype","test_quality","identifier"))
fams <- merge(fams,ff,by=c("stimtype","test_quality","identifier"))
fams <- fams[,c("stimtype","test_quality","identifier",
                          "fam_NA","fam_corr","studyResultId",
                          "workerId","fam_miss")]
fams$studyResultId <- as.character(fams$studyResultId)
fams$workerId <- as.character(fams$workerId)

news <- merge(nna,nc,by=c("stimtype","test_quality","identifier"))
news <- merge(news,nf,by=c("stimtype","test_quality","identifier"))
news <- news[,c("stimtype","test_quality","identifier",
                "new_NA","new_corr","studyResultId","workerId","new_fa")]
news$studyResultId <- as.character(news$studyResultId)
news$workerId <- as.character(news$workerId)

test_dat_compl <- merge(fams,news,by=c("studyResultId","workerId","stimtype","identifier"))
test_dat_compl <- test_dat_compl[,c("studyResultId","workerId","stimtype","identifier",
                                    "fam_NA","fam_corr","fam_miss",
                                    "new_NA","new_corr","new_fa")]
#####
# test_dat_compl is output
```

```{r  include=FALSE}
#  this section is for exclusions
usable <- gnet2_data[,.N,by=.(workerId,studyResultId)]
usable <- usable[N == 160,]
usable <- usable[order(studyResultId),]
usable <- usable[!(duplicated(workerId)),]
usable$identifier <- paste(usable$workerId, "_", usable$studyResultId, sep="")
fineids <- unique(usable$identifier)

study_miss <- gnet2_data[response == "None" & is.na(count_test_sequence), .N, by=c("workerId","studyResultId")]
study_miss$identifier <- paste(study_miss$workerId, "_", study_miss$studyResultId, sep="")

# drop anyone who missed too many responses (>mean+2*sd)
dropbystmiss <- 0 # var how many dropped
limit <- 10
for (i in 1:nrow(study_miss)){
  if (study_miss$N[i] >= limit){
    fineids <- fineids[!fineids == study_miss$identifier[i]]
    dropbystmiss <- dropbystmiss + 1 
  }
}
stmisslimit <- limit # var the miss limit
mean_jds <- mean_jds[identifier %in% fineids]
test_dat_compl <- test_dat_compl[identifier %in% fineids]


# drop anyone who missed too many responses in the test
noresp <- test_dat_compl[,sum(fam_NA, new_NA),by=c("identifier")]

dropbyrtmiss <- 0 # var how many dropped
limit <- 20
for (i in 1:nrow(noresp)){
  if (noresp$V1[i] > limit){
    fineids <- fineids[!fineids == noresp$identifier[i]]
    dropbyrtmiss <- dropbyrtmiss + 1 
  }
}
rtmisslimit <- limit # var the miss limit
mean_jds <- mean_jds[identifier %in% fineids]
test_dat_compl <- test_dat_compl[identifier %in% fineids]

# drop anyone who misjudged prototype - prototype comparisons
dropbymisjud <- 0 

protj <- mean_jds[stimtype == "prototype",]
for (i in 1:nrow(protj)){
  if (protj$V1[i]>5){
    fineids <- fineids[!fineids == protj$identifier[i]]
    dropbymisjud <- dropbymisjud + 1
  }
}
mean_jds <- mean_jds[identifier %in% fineids]
test_dat_compl <- test_dat_compl[identifier %in% fineids]
gnet2_data <- gnet2_data[identifier %in% fineids]
```

# Exclusions

We excluded `r dropbystmiss` participants due to a high number of missed responses in the study phase (<= `r stmisslimit`).

We excluded `r dropbyrtmiss` participants due to low recognition rates (<= `r rtmisslimit`).

We excluded `r dropbymisjud` participants due to inattention to task details as shown by <5 mean difference judged for prototype - prototype comparisons.

This left `r length(unique(mean_jds$identifier))`-`r length(unique(test_dat_compl$identifier))` participants in the analysis.

The identifiers are: `r unique(mean_jds$identifier)`

# Study phase

Participants make a judgement of the difference between a prototype and a novel picture.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
ggplot(mean_jds,aes(x=stimtype,y=V1,color=stimtype)) +
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=5.0, aes( label=round(..y.., digits=3)))
```

# Test phase

Test phase was the same as before: participants see the novel pictures from the study phase with distractors from the same categories. They signal if they think the picture is an old one from the study phase, or a novel distractor.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
# BY RESPONSE TYPE

a <- test_dat_compl$fam_corr
b <- test_dat_compl$new_fa
print(t.test(a,b,paired = TRUE))
print(cohen.d(a,b,paired = TRUE,conf.level=0.95))
d <- with(test_dat_compl, fam_corr - new_fa)
print(shapiro.test(d))

print("Correct recognition for familiars in test")
ggplot(test_dat_compl, aes(x=stimtype, y=fam_corr))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("False alarm for novels in test")
ggplot(test_dat_compl, aes(x=stimtype, y=new_fa))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

test_dat_compl[,CorrectedRecognitions:=fam_corr-new_fa]
test_dat_compl[,CorrectedRejections:=new_corr-fam_miss]
test_dat_compl[,OCCategorizations := CorrectedRecognitions + CorrectedRejections]

print("ANOVA with correct recognition minus false alarm or miss by fam/nov")
a1 <- aov_ez("identifier", "CorrectedRecognitions",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=CorrectedRecognitions, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("ANOVA with correct rejection minus false alarm or miss by fam/nov")
a1 <- aov_ez("identifier", "CorrectedRejections",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=CorrectedRejections, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("ANOVA with corrected differentiation score by category ((crecog-fa)+(creject-fa))")
a1 <- aov_ez("identifier", "OCCategorizations",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=OCCategorizations, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

```

# Mixed models

```{r  include=FALSE}
library(lme4)
library(lmerTest)
library(sjPlot)

lmmdat <- gnet2_data
stlmm <- lmmdat[is.na(test_quality),]
tdlmm <- lmmdat[!(is.na(test_quality)),]
```

## Test phase

### Models #1

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
tdlmm$rt_resp <- NA
tdlmm[response_test_response == "left", rt_resp := 0]
tdlmm[response_test_response == "right", rt_resp := 1]
tdlmm$rt_resp <- as.numeric(tdlmm$rt_resp)
tdlmm$stimtype <- as.factor(tdlmm$stimtype)
tdlmm$trial_quality <- as.factor(tdlmm$trial_quality)
tdlmm$rt_corr <- as.numeric(tdlmm$rt_corr)

logmr <- glmer(rt_resp ~ stimtype * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr)
plot_model(logmr, type = "eff")
plot_model(logmr, type = "int")

logmr2 <- glmer(rt_resp ~ DTF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")
plot_model(logmr2, type = "int")

logmr3 <- glmer(rt_resp ~ DTAF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ DTAN * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")
plot_model(logmr4, type = "int")

logmr5 <- glmer(rt_resp ~ DTN_byPhase * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr5)
plot_model(logmr5, type = "eff")
plot_model(logmr5, type = "int")

# logmr6 <- glmer(rt_resp ~ DTN * tq + (tq|workerId),
#               data = tdlmm,
#                family = binomial)
# summary(logmr6)
# plot_model(logmr6, type = "eff")$DTN
# plot_model(logmr6, type = "eff")$tq
# plot_model(logmr6, type = "int")

tab_model(logmr, logmr2,logmr3,logmr4,logmr5,#logmr6,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)
```

### Models #2

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
tdlmm$total_responses <- scale(tdlmm$total_responses)
logmr <- glmer(rt_resp ~ total_responses + stimtype * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr)
plot_model(logmr, type = "eff")
plot_model(logmr, type = "int")

logmr2 <- glmer(rt_resp ~ total_responses + DTF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")
plot_model(logmr2, type = "int")

logmr3 <- glmer(rt_resp ~ total_responses + DTAF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ total_responses + DTAN * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")
plot_model(logmr4, type = "int")

logmr5 <- glmer(rt_resp ~ total_responses + DTN_byPhase * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr5)
plot_model(logmr5, type = "eff")
plot_model(logmr5, type = "int")

# logmr6 <- glmer(rt_resp ~ DTN * tq + (tq|workerId),
#               data = tdlmm,
#                family = binomial)
# summary(logmr6)
# plot_model(logmr6, type = "eff")$DTN
# plot_model(logmr6, type = "eff")$tq
# plot_model(logmr6, type = "int")

tab_model(logmr, logmr2,logmr3,logmr4,logmr5,#logmr6,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)
```