---
title: "Graded Novelty Enoding Task - 4 shapes version"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
---
```{r  include=FALSE}
source("difference_innumbers.R")

library(ez)
library(ggplot2)
library(emmeans)
library(DescTools)
library(stats)
library(afex)
library(effsize)
library(Hmisc)
```

```{r  include=FALSE}
gnet2_data <- as.data.table(read.csv("alldata_pilot2_alldiffind.csv", encoding = "UTF-8", stringsAsFactors = FALSE))
gnet2_data$DTF <- 0
gnet2_data$DTAF <- 0
gnet2_data$DTAN <- 0
gnet2_data$DTN_byPhase <- 0

for (i in 1:nrow(gnet2_data)){
  for (j in 1:nrow(difference_indices)){
    if (grepl(difference_indices$pict[j],gnet2_data$stim[i])){
      gnet2_data$DTF[i] <- difference_indices$DTF[j]
      gnet2_data$DTAF[i] <- difference_indices$DTAF[j]
      gnet2_data$DTAN[i] <- difference_indices$DTAN[j]
      gnet2_data$DTN_byPhase[i] <- difference_indices$DTN_byPhase[j]
    }
  }
}
# at this point we have all the data with all of the calculated difference indicators
gnet2_data[is.na(st_corr),st_corr := 0]

gnet2_data$identifier <- paste(gnet2_data$workerId, "_", gnet2_data$studyResultId, sep="")

# GENERATE STUDY DT ####
# correct study responses by type
study_dat = gnet2_data[is.na(count_test_sequence), sum(st_corr),
                       by=.(studyResultId,workerId,stimtype)]
# all study trials by type
study_TrialNrByType <- gnet2_data[is.na(count_test_sequence), .N,
                                  by=.(studyResultId,workerId,stimtype)]
strecog <- merge(study_dat,study_TrialNrByType,by=c("studyResultId","workerId","stimtype"))
colnames(strecog) <- c("studyResultId","workerId","stimtype","CCategorization","NrTrials")
# calculate correct categorization rate
strecog[, crrate := CCategorization/NrTrials]
strecog$identifier <- paste(strecog$workerId, "_", strecog$studyResultId, sep="")
rm(study_dat,study_TrialNrByType)
#####

# GENERATE TEST DT ####
test_dat <- gnet2_data[!is.na(count_test_sequence), .N, by=.(studyResultId,workerId,stimtype,test_quality,rt_corr)]

test_dat$identifier <- paste(test_dat$workerId, "_", test_dat$studyResultId, sep="")

mycols  = c("identifier","stimtype","test_quality","rt_corr")
setkeyv(test_dat,mycols)
test_dat_c <- test_dat[J(do.call(CJ,lapply(mycols,function(x)unique(get(x)))))]
for (i in 1:nrow(test_dat_c)){
  if (is.na(test_dat_c$N[i])){
    test_dat_c$N[i] <- 0
  }
}

fna <- test_dat_c[is.na(rt_corr) & test_quality == "fam",]
fna$workerId <- c(fna[,str_split(identifier, pattern = "_")][1])
fna$studyResultId <- c(fna[,str_split(identifier, pattern = "_")][2])
colnames(fna) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","fam_NA","identifier")
fc <- test_dat_c[rt_corr == 1 & test_quality == "fam",]
fc$workerId <- c(fc[,str_split(identifier, pattern = "_")][1])
fc$studyResultId <- c(fc[,str_split(identifier, pattern = "_")][2])
colnames(fc) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","fam_corr","identifier")
ff <- test_dat_c[rt_corr == 0 & test_quality == "fam",]
ff$workerId <- c(ff[,str_split(identifier, pattern = "_")][1])
ff$studyResultId <- c(ff[,str_split(identifier, pattern = "_")][2])
colnames(ff) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","fam_miss","identifier")

nna <- test_dat_c[is.na(rt_corr) & test_quality == "new",]
nna$workerId <- c(nna[,str_split(identifier, pattern = "_")][1])
nna$studyResultId <- c(nna[,str_split(identifier, pattern = "_")][2])
colnames(nna) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","new_NA","identifier")
nc <- test_dat_c[rt_corr == 1 & test_quality == "new",]
nc$workerId <- c(nc[,str_split(identifier, pattern = "_")][1])
nc$studyResultId <- c(nc[,str_split(identifier, pattern = "_")][2])
colnames(nc) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","new_corr","identifier")
nf <- test_dat_c[rt_corr == 0 & test_quality == "new",]
nf$workerId <- c(nf[,str_split(identifier, pattern = "_")][1])
nf$studyResultId <- c(nf[,str_split(identifier, pattern = "_")][2])
colnames(nf) <- c("studyResultId","workerId","stimtype","test_quality","rt_corr","new_fa","identifier")

fams <- merge(fna,fc,by=c("stimtype","test_quality","identifier"))
fams <- merge(fams,ff,by=c("stimtype","test_quality","identifier"))
fams <- fams[,c("stimtype","test_quality","identifier",
                          "fam_NA","fam_corr","studyResultId",
                          "workerId","fam_miss")]
fams$studyResultId <- as.character(fams$studyResultId)
fams$workerId <- as.character(fams$workerId)

news <- merge(nna,nc,by=c("stimtype","test_quality","identifier"))
news <- merge(news,nf,by=c("stimtype","test_quality","identifier"))
news <- news[,c("stimtype","test_quality","identifier",
                "new_NA","new_corr","studyResultId","workerId","new_fa")]
news$studyResultId <- as.character(news$studyResultId)
news$workerId <- as.character(news$workerId)

test_dat_compl <- merge(fams,news,by=c("studyResultId","workerId","stimtype","identifier"))
test_dat_compl <- test_dat_compl[,c("studyResultId","workerId","stimtype","identifier",
                                    "fam_NA","fam_corr","fam_miss",
                                    "new_NA","new_corr","new_fa")]
rm(nc,nf,news,nna,fc,ff,fna,fams)
#####

# strecog & test_dat_compl holds the data from st and rt
```

```{r  include=FALSE}
#  this section is for exclusions
total_runs <- nrow(gnet2_data[,.N,by=.(workerId,studyResultId)])
usable <- gnet2_data[,.N,by=.(workerId,studyResultId)]
usable <- usable[N == 175,]
usable <- usable[order(studyResultId),]
usable <- usable[!(duplicated(workerId)),]
usable$identifier <- paste(usable$workerId, "_", usable$studyResultId, sep="")
fineids <- unique(usable$identifier)

crates <- strecog[stimtype == "prototype",c("identifier","crrate")]

####
StudySummary <- gnet2_data[is.na(count_test_sequence) & response == "left" & stimtype == "prototype", .N/25, by=.(workerId,studyResultId)]
StudyFA <- gnet2_data[is.na(count_test_sequence) & response == "left" & stimtype != "prototype", .N/50, by=.(workerId,studyResultId)]
StudyCR <- merge(StudySummary, StudyFA,by=c("workerId","studyResultId"), all = TRUE)
colnames(StudyCR) <- c("workerId","studyResultId","R","FA")
StudyCR[is.na(FA), FA:=0]
StudyCR[,CR := R - FA]
rm(StudySummary,StudyFA)

StudyBinom <- gnet2_data[is.na(count_test_sequence) & response == "left",.(workerId,studyResultId,response,stimtype),]
StudyBinom$RespBinomial <- 0
StudyBinom[stimtype == "prototype", RespBinomial := 1]
handles <- unique(StudyBinom[,.(workerId,studyResultId)])
StudyCR$CI_lower <- 0
StudyCR$CI_upper <- 0
for (i in 1:nrow(handles)){
  tempBinData <- StudyBinom[workerId == handles$workerId[i] & studyResultId == handles$studyResultId[i],RespBinomial]
  confint <- binconf(x=sum(tempBinData), n=length(tempBinData))
  StudyCR[workerId == handles$workerId[i] & studyResultId == handles$studyResultId[i], CI_lower := confint[2]]
  StudyCR[workerId == handles$workerId[i] & studyResultId == handles$studyResultId[i], CI_upper := confint[3]]
}

insufficient_data <- nrow(StudyCR) - nrow(usable)
StudyCR <- StudyCR[workerId %in% usable$workerId & studyResultId %in% usable$studyResultId,]

# exclusion crit based on corrected recog rate
StudySummary <- StudyCR[CR > 0] # 0.3 is the 20th percentile
# exclusion crit based on uncorrected recog rate
# StudySummary <- StudySummary[V1 > 0.5]
StudySummary <- StudyCR[CI_lower > 0.33]

ExcludePrototypeRecog <- nrow(StudyCR) - nrow(StudySummary)
StudySummary$identifier <- paste(StudySummary$workerId, "_", StudySummary$studyResultId, sep="")

strecog <- strecog[identifier %in% StudySummary$identifier,]
test_dat_compl <- test_dat_compl[identifier %in% StudySummary$identifier,]
gnet2_data <- gnet2_data[identifier %in% StudySummary$identifier,]

# we need to add some zeros for the type*tq*rkey(response) combinations that are left out
# this will be done after exclusions

norespfam <- test_dat_compl[,sum(fam_NA),by=c("identifier")]
norespnew <- test_dat_compl[,sum(new_NA),by=c("identifier")]
noresp <- merge(norespfam, norespnew, by=c("identifier"))
noresp[,nor := V1.x + V1.y]

nrlimit <- 20 # var the miss limit
noresp_ok <- noresp[nor <= nrlimit]
dropbynoresp <- nrow(noresp) - nrow(noresp_ok)

strecog <- strecog[identifier %in% noresp_ok$identifier]
test_dat_compl <- test_dat_compl[identifier %in% noresp_ok$identifier]
gnet2_data <- gnet2_data[identifier %in% noresp_ok$identifier]
```

# Exclusions

In total, the task was run `r total_runs` times.

`r insufficient_data` runs were not completed or were duplicates.

We excluded `r ExcludePrototypeRecog` participants due to low performance in the study phase. We calculated the confidence intervals for the probability of correct "old" responses and excluded those participants whose lower CI was below 0.33 (chance level - 25 opportunities for correct "old" response, 50 for incorrect).

We excluded `r dropbynoresp` participants due to missed responses in test phase (<= `r nrlimit`).

This left `r length(unique(strecog$identifier))` participants in the analysis.

```{r  include=FALSE}

gnet2_register <- as.data.table(read.csv("gnet_v2_-_register.csv", encoding = "UTF-8", stringsAsFactors = FALSE))
colnames(gnet2_register) <- c("datetime","workerId","age","gen",
                              "health","sleep","coffee","smoke","alcdrug")

gnet2_register <- gnet2_register[workerId %in% gnet2_data$workerId]
gnet2_register <- gnet2_register[!(duplicated(workerId)),]
```

The sample had a mean(±sd) age of `r mean(gnet2_register$age)` ± `r sd(gnet2_register$age)`.

The sample contained `r nrow(gnet2_register[gen == "Nő",])` women.

# Comparison with GNET 1

```{r  include=FALSE}
gnet_data <- as.data.table(read.csv("gnet1_raw_data.csv"))
gnet_data$st_corr <- 0
gnet_data[type == "prototype" & response == "left", st_corr := 1]
gnet_data[type != "prototype" & response == "right", st_corr := 1]
gnet1_study_dat <- gnet_data[is.na(count_test_sequence), sum(st_corr),
                       by=.(studyResultId,workerId,type)]
temp <- gnet_data[is.na(count_test_sequence), .N,
                       by=.(studyResultId,workerId,type)]
gnet1_study_dat <- merge(gnet1_study_dat, temp, by=c("studyResultId","workerId","type"))
colnames(gnet1_study_dat) <- c("studyResultId","workerId","type","CCategorization","NrTrials")
gnet1_study_dat[,ccrate := CCategorization/NrTrials]
rm(temp)

# GENERATE TEST DT ####
gnet_data$rt_corr <- 0
gnet_data[tq == "old" & response == "left", rt_corr :=1]
gnet_data[tq == "new" & response == "right", rt_corr :=1]
gnet_data[response == "down", rt_corr := NA]
gnet_data[response == "None", rt_corr := NA]

gnet1_test_dat <- gnet_data[!is.na(count_test_sequence), .N, by=.(studyResultId,workerId,type,tq,rt_corr)]

# fill out nonexistent
gnet1_test_dat$identifier <- paste(gnet1_test_dat$workerId, "_", gnet1_test_dat$studyResultId, sep="")
mycols  = c("identifier","type","tq","rt_corr")
setkeyv(gnet1_test_dat,mycols)
gnet1_test_dat <- gnet1_test_dat[J(do.call(CJ,lapply(mycols,function(x)unique(get(x)))))]
for (i in 1:nrow(gnet1_test_dat)){
  if (is.na(gnet1_test_dat$N[i])){
    gnet1_test_dat$N[i] <- 0
    gnet1_test_dat$workerId[i] <- str_split(gnet1_test_dat$identifier[i], pattern = "_")[[1]][1]
    gnet1_test_dat$studyResultId[i] <- str_split(gnet1_test_dat$identifier[i], pattern = "_")[[1]][2]
  }
}

old <- gnet1_test_dat[tq == "old",]
new <- gnet1_test_dat[tq == "new",]
oldcorr <- old[rt_corr == 1,]
colnames(oldcorr) <- c("studyResultId","workerId","type","tq","rt_corr","fam_corr","identifier")
oldcorr <- oldcorr[,c("studyResultId","workerId","type","fam_corr")]
oldmiss <- old[rt_corr == 0,]
colnames(oldmiss) <- c("studyResultId","workerId","type","tq","rt_corr","fam_miss","identifier")
oldmiss <- oldmiss[,c("studyResultId","workerId","type","fam_miss")]
newcorr <- new[rt_corr == 1,]
colnames(newcorr) <- c("studyResultId","workerId","type","tq","rt_corr","new_corr","identifier")
newcorr <- newcorr[,c("studyResultId","workerId","type","new_corr")]
newmiss <- new[rt_corr == 0,]
colnames(newmiss) <- c("studyResultId","workerId","type","tq","rt_corr","new_fa","identifier")
newmiss <- newmiss[,c("studyResultId","workerId","type","new_fa")]

old <- merge(oldcorr,oldmiss,by=c("studyResultId","workerId","type"))
new <- merge(newcorr,newmiss,by=c("studyResultId","workerId","type"))
gnet1_test_dat <- merge(old,new,by=c("studyResultId","workerId","type"))
rm(oldcorr,oldmiss,newcorr,newmiss,old,new)
```

The recognition of the prototypes compared between studies (original GNET with 5 shapes).

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
a <- gnet1_study_dat[type == "prototype", ccrate]
b <- strecog[stimtype == "prototype", crrate]
print(t.test(a,b,paired = FALSE))
print(cohen.d(a,b,paired = FALSE,conf.level=0.95))
```

The distribution of the data is not normal (original GNET):

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
print(shapiro.test(a))
```

The distribution of the data is not normal (current GNET):

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
print(shapiro.test(b))
```

Use a non-parametric alternative for the Welch test - Mann-Whitney-Wilcoxon U test

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
print(wilcox.test(a,b,conf.int=TRUE))
```

The overall correct categorizations in the test phase

```{r  include=FALSE}

gnet1_test_dat[,famcat := fam_corr - new_fa]
gnet1_test_dat[,newcat := new_corr - fam_miss]
gnet1_test_dat[,occ := famcat + newcat]
a <- gnet1_test_dat[,mean(occ),by=workerId]
a <- a$V1

gnet2_test_dat <- test_dat_compl
gnet2_test_dat[,famcat := fam_corr - new_fa]
gnet2_test_dat[,newcat := new_corr - fam_miss]
gnet2_test_dat[,occ := famcat + newcat]
b <- gnet2_test_dat[,mean(occ),by=workerId]
b <- b$V1

```

The distribution of the test data is not normal (original GNET):

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
print(shapiro.test(a))
```

The distribution of the test data is not normal (current GNET):

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
print(shapiro.test(b))
```

The performance on the recognition test compared with a Welch test

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
print(t.test(a,b,paired = FALSE))
print(cohen.d(a,b,paired = FALSE,conf.level=0.95))
```

# Study phase

ANOVA to compare the rejection rate for each difference category; plot shows the prototype recog rate also.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

# We use an ANOVA to see if there is a difference in correct rejection for the different novels.
# csak az újakra adott válaszok

# ezANOVA(study_dat_news, dv =  crrate, within = type, wid = workerId)
a1 <- aov_ez("identifier", "crrate",
             strecog[stimtype != "prototype"], within = "stimtype")
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
contrast(m3, "poly")


ggplot(strecog, aes(x=stimtype, y=crrate, color = stimtype)) + 
  geom_jitter(width=0.2, alpha=0.2) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=5.0, aes( label=round(..y.., digits=3)))


```

# Test phase

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

# BY RESPONSE TYPE

a <- test_dat_compl$fam_corr
b <- test_dat_compl$new_fa
print(t.test(a,b,paired = TRUE))
print(cohen.d(a,b,paired = TRUE,conf.level=0.95))
d <- with(test_dat_compl, fam_corr - new_fa)
print(shapiro.test(d))

print("Correct recognition for familiars in test")
ggplot(test_dat_compl, aes(x=stimtype, y=fam_corr))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("False alarm for novels in test")
ggplot(test_dat_compl, aes(x=stimtype, y=new_fa))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

test_dat_compl[,CorrectedRecognitions:=fam_corr-new_fa]
test_dat_compl[,CorrectedRejections:=new_corr-fam_miss]
test_dat_compl[,OCCategorizations := CorrectedRecognitions + CorrectedRejections]

print("ANOVA with correct recognition minus false alarm or miss by fam/nov")
a1 <- aov_ez("identifier", "CorrectedRecognitions",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=CorrectedRecognitions, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("ANOVA with correct rejection minus false alarm or miss by fam/nov")
a1 <- aov_ez("identifier", "CorrectedRejections",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=CorrectedRejections, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))

print("ANOVA with corrected differentiation score by category ((crecog-fa)+(creject-fa))")
a1 <- aov_ez("identifier", "OCCategorizations",
             test_dat_compl, within = c("stimtype"))
a1
m3 <- emmeans(a1, ~ stimtype)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(test_dat_compl, aes(x=stimtype, y=OCCategorizations, color=stimtype))+
  geom_jitter(width=0.2, alpha=0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3)))


```

# Mixed models

```{r  include=FALSE}
library(lme4)
library(lmerTest)
library(sjPlot)


lmmdat <- gnet2_data

stlmm <- lmmdat[is.na(test_quality),]

tdlmm <- lmmdat[!(is.na(test_quality)),]


```

## Test phase

### Models #1

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
tdlmm$rt_resp <- NA
tdlmm[response_test_response == "left", rt_resp := 0]
tdlmm[response_test_response == "right", rt_resp := 1]
tdlmm$rt_resp <- as.numeric(tdlmm$rt_resp)
tdlmm$stimtype <- as.factor(tdlmm$stimtype)
tdlmm$trial_quality <- as.factor(tdlmm$trial_quality)
tdlmm$rt_corr <- as.numeric(tdlmm$rt_corr)

logmr <- glmer(rt_resp ~ stimtype * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial,
               control = lmerControl(optCtrl=list(xtol_abs=1e-8, ftol_abs=1e-8, maxeval=100000)))
summary(logmr)
plot_model(logmr, type = "eff")
plot_model(logmr, type = "int")

logmr2 <- glmer(rt_resp ~ DTF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")
plot_model(logmr2, type = "int")

logmr3 <- glmer(rt_resp ~ DTAF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ DTAN * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")
plot_model(logmr4, type = "int")

logmr5 <- glmer(rt_resp ~ DTN_byPhase * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr5)
plot_model(logmr5, type = "eff")
plot_model(logmr5, type = "int")

# logmr6 <- glmer(rt_resp ~ DTN * tq + (tq|workerId),
#               data = tdlmm,
#                family = binomial)
# summary(logmr6)
# plot_model(logmr6, type = "eff")$DTN
# plot_model(logmr6, type = "eff")$tq
# plot_model(logmr6, type = "int")

tab_model(logmr, logmr2,logmr3,logmr4,logmr5,#logmr6,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)
```

### Models #2

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
tdlmm$total_responses <- scale(tdlmm$total_responses)
logmr <- glmer(rt_resp ~ total_responses + stimtype * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr)
plot_model(logmr, type = "eff")
plot_model(logmr, type = "int")

logmr2 <- glmer(rt_resp ~ total_responses + DTF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")
plot_model(logmr2, type = "int")

logmr3 <- glmer(rt_resp ~ total_responses + DTAF * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ total_responses + DTAN * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")
plot_model(logmr4, type = "int")

logmr5 <- glmer(rt_resp ~ total_responses + DTN_byPhase * test_quality + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr5)
plot_model(logmr5, type = "eff")
plot_model(logmr5, type = "int")

# logmr6 <- glmer(rt_resp ~ DTN * tq + (tq|workerId),
#               data = tdlmm,
#                family = binomial)
# summary(logmr6)
# plot_model(logmr6, type = "eff")$DTN
# plot_model(logmr6, type = "eff")$tq
# plot_model(logmr6, type = "int")

tab_model(logmr, logmr2,logmr3,logmr4,logmr5,#logmr6,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)
```