---
title: "Graded Novelty Encoding Task - original vs narrative"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
---
# The paradigm

We compare the results of the original GNET study with the contextualized one.

```{r  include=FALSE}
library(ez)
library(ggplot2)
library(emmeans)
library(DescTools)
library(stats)
library(afex)
library(effsize)
library(lubridate)
library(Hmisc)
source("difference_innumbers_bydim.R")
source("datproc_1strun_bydim.R")
source("datproc_2ndrun_bydim.R")
GNET_pilot_alldata <- rbind(GNET_pilot_RUN1_alldata,GNET_pilot_RUN2_alldata)
rm(GNET_pilot_RUN1_alldata,GNET_pilot_RUN2_alldata)

# EXCLUSIONs ####

# extract the number of all separate runs - allruns
allruns <- unique(GNET_pilot_alldata[,c("studyResultId","workerId")])
allruns <- na.omit(allruns)
allruns <- nrow(allruns)

# REMOVE INSUFFICIENT DATA
ids <- GNET_pilot_alldata[, .(rowCount = .N), by = c("workerId","studyResultId","datetime")]
ids[,RUNIDENTIFIER := paste(ids$workerId, "_", ids$studyResultId, sep="")]
ids <- ids[rowCount >= 175]
GNET_pilot_alldata <-
  GNET_pilot_alldata[workerId %in% ids$workerId & studyResultId %in% ids$studyResultId,]
GNET_pilot_alldata <- 
  GNET_pilot_alldata[!duplicated(GNET_pilot_alldata),]
completeruns <- nrow(ids)

# REMOVE TOO MUCH MISSED RESPONSES
ResponsesSummary <- GNET_pilot_alldata[, .(rowCount = .N), by = .(workerId,studyResultId,type,tq,response)]
MissedResSummary <- ResponsesSummary[response == "None", sum(rowCount),by = .(workerId,studyResultId)]
MissedResSummary <- MissedResSummary[V1 < 66,]
GNET_pilot_alldata <-
  GNET_pilot_alldata[(workerId %in% MissedResSummary$workerId) & (studyResultId %in% MissedResSummary$studyResultId),]
# Nr of exclusions due to misses
ExcludeMisses <- nrow(ids) - nrow(MissedResSummary)

# túl alacsony prototype recog rate a study alatt kipottyan
StudySummary <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left" & type == "prototype", .N/25, by=.(workerId,studyResultId)]
StudyFA <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left" & type != "prototype", .N/50, by=.(workerId,studyResultId)]
StudyCR <- merge(StudySummary, StudyFA,by=c("workerId","studyResultId"), all = TRUE)
colnames(StudyCR) <- c("workerId","studyResultId","R","FA")
StudyCR[is.na(FA), FA:=0]
StudyCR[,CR := R - FA]

StudyBinom <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left",.(workerId,studyResultId,response,type),]
StudyBinom$RespBinomial <- 0
StudyBinom[type == "prototype", RespBinomial := 1]
handles <- unique(StudyBinom[,.(workerId,studyResultId)])
StudyCR$CI_lower <- 0
StudyCR$CI_upper <- 0
for (i in 1:nrow(handles)){
  tempBinData <- StudyBinom[workerId == handles$workerId[i] & studyResultId == handles$studyResultId[i],RespBinomial]
  confint <- binconf(x=sum(tempBinData), n=length(tempBinData))
  StudyCR[workerId == handles$workerId[i] & studyResultId == handles$studyResultId[i], CI_lower := confint[2]]
  StudyCR[workerId == handles$workerId[i] & studyResultId == handles$studyResultId[i], CI_upper := confint[3]]
}

# exclusion crit based on corrected recog rate
StudySummary <- StudyCR[CR > 0] # 0.3 is the 20th percentile
# exclusion crit based on uncorrected recog rate
# StudySummary <- StudySummary[V1 > 0.5]
StudySummary <- StudyCR[CI_lower > 0.33]
ExcludePrototypeRecog <- nrow(MissedResSummary) - nrow(StudySummary)
GNET_pilot_alldata <- GNET_pilot_alldata[(workerId %in% StudySummary$workerId) & (studyResultId %in% MissedResSummary$studyResultId),]

# túl sok maybe response kipottyan
TestSummary <- GNET_pilot_alldata[!is.na(count_test_sequence) & response == "down", .N, by=.(workerId,studyResultId)]
TestSummary <- TestSummary[N < 50]
ExcludeMaybeResp <- nrow(StudySummary) - nrow(TestSummary)
GNET_pilot_alldata <-
  GNET_pilot_alldata[(workerId %in% TestSummary$workerId) & (studyResultId %in% MissedResSummary$studyResultId),]

GNET_pilot_filtered <- GNET_pilot_alldata

rm(GNET_pilot_alldata,ids,MissedResSummary,ResponsesSummary,StudySummary)
#### exclude those cases where a participant completed multiple runs (only first is kept)
multipleruns <- GNET_pilot_filtered[,sum(DTF),by=.(workerId,studyResultId,datetime)]
multipleruns$datetime <- mdy_hms(multipleruns$datetime)
mrs <- c(multipleruns$workerId[duplicated(multipleruns$workerId)])
for (i in 1:length(mrs)){
  temp <- multipleruns[workerId == mrs[i]]
  first <- min(temp$datetime)
  temp <- temp[datetime != first,]
  GNET_pilot_filtered <- GNET_pilot_filtered[!(workerId %in% temp & studyResultId %in% temp),]
}
rm(temp,first,multipleruns)
ExcludeMRuns <- length(mrs)
rm(mrs)
#####
```

# Participants

## Original GNET

The online task has been started a total of `r allruns` times.

We excluded a total of `r allruns - completeruns` runs due to irregular data leaving `r completeruns` in the analysis.

We excluded some (`r ExcludeMisses`) runs as they missed more than 66 of 175 trials.

We also excluded `r ExcludePrototypeRecog` runs in which the participant produced less than 0.3 corrected recognition rate for familiars in the study phase.

We also excluded `r ExcludeMaybeResp` participants as they overused "maybe" responses in the test phase (more than 25).

We also excluded `r ExcludeMRuns` run(s) as only the first run is kept in the analysis from one participant.

This left a total of `r nrow(GNET_pilot_filtered)/175` participants.

Maybe responses [mean(±sd)] : `r mean(TestSummary$N)` ± `r sd(TestSummary$N)`

```{r  include=FALSE}
source("registerdata_in.R")

jkwid <- jkwid[X.U.FEFF.id %in% TestSummary$workerId]
registernmail <- registernmail[X.U.FEFF.id %in% TestSummary$workerId]

jkwid <- jkwid[,c("age","gen")]
registernmail <- registernmail[,c("age","gen")]

demog <- rbind(jkwid,registernmail)
rm(jkwid,registernmail)

```

The sample had a mean(±sd) age of `r mean(demog$age)` ± `r sd(demog$age)`.

The sample contained `r sum(demog$gen)` women.

## Art narrative

```{r  include=FALSE}
source("datproc_artnarr_bydim.R")
GNET_pilot_alldata <- GNET_artn_alldata
rm(GNET_artn_alldata)
# EXCLUSIONs ####

# extract the number of all separate runs - allruns
allruns <- unique(GNET_pilot_alldata[,c("multichar_knowresp","sessionid")])
allruns <- na.omit(allruns)
allruns <- nrow(allruns)

# REMOVE INSUFFICIENT DATA
ids <- GNET_pilot_alldata[, .(rowCount = .N), by = c("multichar_knowresp","sessionid")]
ids[,RUNIDENTIFIER := paste(ids$multichar_knowresp, "_", ids$sessionid, sep="")]
ids <- ids[rowCount >= 175]
GNET_pilot_alldata <-
  GNET_pilot_alldata[multichar_knowresp %in% ids$multichar_knowresp & sessionid %in% ids$sessionid,]
GNET_pilot_alldata <- 
  GNET_pilot_alldata[!duplicated(GNET_pilot_alldata),]
completeruns <- nrow(ids)

# REMOVE TOO MUCH MISSED RESPONSES
ResponsesSummary <- GNET_pilot_alldata[, .(rowCount = .N), by = .(multichar_knowresp,sessionid,type,tq,response)]
MissedResSummary <- ResponsesSummary[response == "None", sum(rowCount),by = .(multichar_knowresp,sessionid)]
MissedResSummary <- MissedResSummary[V1 < 66,]
GNET_pilot_alldata <-
  GNET_pilot_alldata[(multichar_knowresp %in% MissedResSummary$multichar_knowresp) & (sessionid %in% MissedResSummary$sessionid),]
# Nr of exclusions due to misses
ExcludeMisses <- nrow(ids) - nrow(MissedResSummary)

# túl alacsony prototype recog rate a study alatt kipottyan
StudySummary <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left" & type == "prototype", .N/25, by=.(multichar_knowresp,sessionid)]
StudyFA <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left" & type != "prototype", .N/50, by=.(multichar_knowresp,sessionid)]
StudyCR <- merge(StudySummary, StudyFA,by=c("multichar_knowresp","sessionid"), all = TRUE)
colnames(StudyCR) <- c("multichar_knowresp","sessionid","R","FA")
StudyCR[is.na(FA), FA:=0]
StudyCR[,CR := R - FA]

StudyBinom <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left",.(multichar_knowresp,sessionid,response,type),]
StudyBinom$RespBinomial <- 0
StudyBinom[type == "prototype", RespBinomial := 1]
handles <- unique(StudyBinom[,.(multichar_knowresp,sessionid)])
StudyCR$CI_lower <- 0
StudyCR$CI_upper <- 0
for (i in 1:nrow(handles)){
  tempBinData <- StudyBinom[multichar_knowresp == handles$multichar_knowresp[i] & sessionid == handles$sessionid[i],RespBinomial]
  confint <- binconf(x=sum(tempBinData), n=length(tempBinData))
  StudyCR[multichar_knowresp == handles$multichar_knowresp[i] & sessionid == handles$sessionid[i], CI_lower := confint[2]]
  StudyCR[multichar_knowresp == handles$multichar_knowresp[i] & sessionid == handles$sessionid[i], CI_upper := confint[3]]
}

# exclusion crit based on corrected recog rate
StudySummary <- StudyCR[CR > 0] # 0.3 is the 20th percentile
# exclusion crit based on uncorrected recog rate
# StudySummary <- StudySummary[V1 > 0.5]
StudySummary <- StudyCR[CI_lower > 0.33]
ExcludePrototypeRecog <- nrow(MissedResSummary) - nrow(StudySummary)
GNET_pilot_alldata <- GNET_pilot_alldata[(multichar_knowresp %in% StudySummary$multichar_knowresp) & (sessionid %in% MissedResSummary$sessionid),]

# túl sok maybe response kipottyan
TestSummary <- GNET_pilot_alldata[!is.na(count_test_sequence) & response == "down", .N, by=.(multichar_knowresp,sessionid)]
TestSummary <- TestSummary[N < 50]
ExcludeMaybeResp <- nrow(StudySummary) - nrow(TestSummary)
GNET_pilot_alldata <-
  GNET_pilot_alldata[(multichar_knowresp %in% TestSummary$multichar_knowresp) & (sessionid %in% MissedResSummary$sessionid),]

GNET_artn_filtered <- GNET_pilot_alldata

rm(GNET_pilot_alldata,ids,MissedResSummary,ResponsesSummary,StudySummary)

# some neptun ids are messed up
for (i in 1:nrow(GNET_artn_filtered)){
  if (GNET_artn_filtered$multichar_knowresp[i] == "capsmlcqiycaps"){
    GNET_artn_filtered$multichar_knowresp[i] <- "mlcqiy"
  }
  if (GNET_artn_filtered$multichar_knowresp[i] == "capsb2capsd8capsb2"){
    GNET_artn_filtered$multichar_knowresp[i] <- "b2d8b2"
  }
}
#####
```

```{r  include=FALSE}
source("regdata-artnarr_in.R")

# we need to remove the data where personal info is not available
jkn <- unique(tolower(jkwid$NEPTUN))
bdn <- unique(GNET_artn_filtered$multichar_knowresp)
# this gives usable neptuns
KEEP <- bdn[bdn %in% jkn]
rm(jkn,bdn)
# only keep these in both data tables
GNET_artn_filtered <- GNET_artn_filtered[multichar_knowresp %in% KEEP]
jkwid <- jkwid[tolower(NEPTUN) %in% KEEP]
jkwid <- jkwid[!duplicated(jkwid$NEPTUN)]

demog <- jkwid[,c("age","gen")]
demog[gen == "Nő", gen := 1]
demog[gen == "Férfi", gen := 0]
demog$gen <- as.numeric(demog$gen)
```

The online task has been started a total of `r allruns` times.

We excluded a total of `r allruns - completeruns` runs due to irregular data leaving `r completeruns` in the analysis.

We excluded some (`r ExcludeMisses`) runs as they missed more than 66 of 175 trials.

We also excluded `r ExcludePrototypeRecog` runs in which the participant produced less than 0.3 corrected recognition rate for familiars in the study phase.

We also excluded `r ExcludeMaybeResp` participants as they overused "maybe" responses in the test phase (more than 25).

This left a total of `r nrow(GNET_artn_filtered)/175` participants.

Maybe responses [mean(±sd)] : `r mean(TestSummary$N)` ± `r sd(TestSummary$N)`

The sample had a mean(±sd) age of `r mean(demog$age)` ± `r sd(demog$age)`.

The sample contained `r sum(demog$gen)` women.

```{r  include=FALSE}
source("means_1strun.R")
Study_CorrRejectionByType_1R <- Study_CorrRejectionByType
Study_ResponsesByType_1R <- Study_ResponsesByType
Test_ResponsesByType_1R <- Test_ResponsesByType
rm(Study_CorrRejectionByType,Study_ResponsesByType,Test_ResponsesByType)

source("means_2ndrun.R")
Study_CorrRejectionByType_2R <- Study_CorrRejectionByType
Study_ResponsesByType_2R <- Study_ResponsesByType
Test_ResponsesByType_2R <- Test_ResponsesByType
rm(Study_CorrRejectionByType,Study_ResponsesByType,Test_ResponsesByType)

GNET_orig_safe <- GNET_pilot_filtered
GNET_pilot_filtered <- GNET_artn_filtered
source("means_artnarr202301.R")
Study_CorrRejectionByType_AN <- Study_CorrRejectionByType
Study_ResponsesByType_AN <- Study_ResponsesByType
Test_ResponsesByType_AN <- Test_ResponsesByType
rm(Study_CorrRejectionByType,Study_ResponsesByType,Test_ResponsesByType)

# not yet clear why, but this seems unnecessary

# unite the data from the two runs
# Study_CorrRejectionByType <- rbind(Study_CorrRejectionByType_1R,Study_CorrRejectionByType_2R)
# Study_ResponsesByType <- rbind(Study_ResponsesByType_1R,Study_ResponsesByType_2R)
# Test_ResponsesByType <- rbind(Test_ResponsesByType_1R,Test_ResponsesByType_2R)
# rm(Study_CorrRejectionByType_1R,Study_CorrRejectionByType_2R,
#    Study_ResponsesByType_1R,Study_ResponsesByType_2R,
#    Test_ResponsesByType_1R,Test_ResponsesByType_2R)

# add study id column to DTs
Study_CorrRejectionByType_1R$stid <- "orig"
Study_ResponsesByType_1R$stid <- "orig"
Test_ResponsesByType_1R$stid <- "orig"
  
Study_CorrRejectionByType_AN$stid <- "artn"
colnames(Study_CorrRejectionByType_AN) <- c("response","workerId","type","N","stid")
Study_ResponsesByType_AN$stid <- "artn"
colnames(Study_ResponsesByType_AN) <- c("response","workerId","type","N","stid")
Test_ResponsesByType_AN$stid <- "artn"
colnames(Test_ResponsesByType_AN) <- c("workerId","type","maybe_O","noresp_O","recog_O","miss_O","maybe_N","noresp_N","fa_N","reject_N","CorrRecog","CorrRejec","OverallCCat","stid")

# unite the data from the two studies
Study_CorrRejectionByType <- rbind(Study_CorrRejectionByType_1R,Study_CorrRejectionByType_AN)
Study_ResponsesByType <- rbind(Study_ResponsesByType_1R,Study_ResponsesByType_AN)
Test_ResponsesByType <- rbind(Test_ResponsesByType_1R,Test_ResponsesByType_AN)
rm(Study_CorrRejectionByType_1R,Study_CorrRejectionByType_2R,Study_CorrRejectionByType_AN,Study_ResponsesByType_1R,Study_ResponsesByType_2R,Study_ResponsesByType_AN,
   Test_ResponsesByType_1R,Test_ResponsesByType_2R,Test_ResponsesByType_AN)
```

# Study phase:

During the study phase, the participants see familiar and novel items.

We use an ANOVA to see if there is a difference in correct rejection for the different novels.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
# ezANOVA(study_dat_news, dv =  crrate, within = type, wid = workerId)
a1 <- aov_ez("workerId", "N",
             Study_CorrRejectionByType, within = "type", between = "stid")
a1
m3 <- emmeans(a1, ~ type * stid)
pairs(m3)
contrast(m3, "poly")
ggplot(Study_CorrRejectionByType[stid == "orig"], aes(x=type, y=N, color = type)) + 
  geom_jitter(width=0.2, alpha=0.2) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "fully novel", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel color combinations")) + 
  ggtitle("Number of correct rejections in the study phase by novel picture category") +
  xlab("") +
  ylab("Nr of correct rejections") +
  theme(legend.position = "none")

ggplot(Study_CorrRejectionByType[stid == "artn"], aes(x=type, y=N, color = type)) + 
  geom_jitter(width=0.2, alpha=0.2) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "fully novel", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel color combinations")) + 
  ggtitle("Number of correct rejections in the study phase by novel picture category") +
  xlab("") +
  ylab("Nr of correct rejections") +
  theme(legend.position = "none")
```

# Test phase:

This phase tests the learning that has occurred during the study phase. If the participants learned the novels in the study phase, their responses should differ for the stimuli that they have already seen during the study phase (familiars) and those that they see for the first time during the test phase (novels).

```{r  warning=FALSE, echo=FALSE}
library(rstatix)
```

## ANOVA - Corrected Recog

```{r  warning=FALSE, echo=FALSE}

Test_ResponsesByType$neworder <- ""
Test_ResponsesByType[type == "diffarr", neworder := "A"]
Test_ResponsesByType[type == "sarr", neworder := "B"]
Test_ResponsesByType[type == "sarrcol", neworder := "D"]
Test_ResponsesByType[type == "sarrsha", neworder := "C"]
Test_ResponsesByType[type == "sarrshacol", neworder := "E"]

setorder(Test_ResponsesByType, neworder)

a1 <- aov_ez("workerId", "CorrRecog",
             Test_ResponsesByType, within = c("neworder"), between = "stid")
a1
m3 <- emmeans(a1, ~ neworder * stid)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(Test_ResponsesByType[stid == "orig"], aes(x=neworder, y=CorrRecog, color=neworder))+
  geom_jitter(width=0.3, alpha=0.3) +
  stat_summary(geom = "errorbar", fun.data = mean_se, col = "black", width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("A" = "fully novel", "B" = "novel shapes & colors",
                              "D" = "novel shapes", "C" = "novel colors", "E" = "novel color combinations")) +
  ggtitle("Corrected recognition score in the test phase by picture category")+
  xlab("")+
  ylab("")+
  theme(legend.position = "none")

ggplot(Test_ResponsesByType[stid == "artn"], aes(x=neworder, y=CorrRecog, color=neworder))+
  geom_jitter(width=0.3, alpha=0.3) +
  stat_summary(geom = "errorbar", fun.data = mean_se, col = "black", width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("A" = "fully novel", "B" = "novel shapes & colors",
                              "D" = "novel shapes", "C" = "novel colors", "E" = "novel color combinations")) +
  ggtitle("Corrected recognition score in the test phase by picture category")+
  xlab("")+
  ylab("")+
  theme(legend.position = "none")

ndf <- a1$anova_table$`num Df`
ddf <- a1$anova_table$`den Df`
p <- a1$anova_table$`Pr(>F)`
```

ANOVA (factor: TYPE (5 lvls)): (F[`r ndf`,`r ddf`] = `r a1$anova_table$F`, p = `r p`, n2G = `r a1$anova_table$ges`).

# Mixed models

The metrics

-DTF - Difference To corresponding Familiar picture
All pictures are compared to a familiar. The number of differences between the three vectors of the pictures yields a difference score.

-DTAF - mean Difference To All Familiars
We calculate the difference from all prototypes and take the mean for each picture in the set.

-DTN - mean Difference To all other Novels in the same category
We calculate the differences between each pair of pictures and then take the mean of these differences (19 comparisons per stim).


```{r  include=FALSE}
library(lme4)
library(lmerTest)
library(sjPlot)

GNET_artn_filtered$stid <- "artn"
colnames(GNET_artn_filtered) <- c("count_study_sequence","count_test_sequence","datetime","response","response_study_response","response_test_response","response_time","response_time_study_response","response_time_test_response","stim","workerId","studyResultId","type","tq","DTF","ColDTF","ShaDTF","ArrDTF","DTAF","ColDTAF","ShaDTAF","ArrDTAF","DTAN","ColDTAN","ShaDTAN","ArrDTAN","DTN_byPhase","ColDTN_bP","ShaDTN_bP","ArrDTN_bP","DTN","stid")
GNET_orig_safe$stid <- "orig"
GNET_orig_safe[,batchId := NULL]
GNET_orig_safe[,batchTitle := NULL]

# we use a preprocessed DT which holds the data of the 59 participants that were not thrown out
lmmdat <- rbind(GNET_artn_filtered,GNET_orig_safe)

# lmmdat$DTF <- scale(lmmdat$DTF)
# lmmdat$DTAF <- scale(lmmdat$DTAF)
# lmmdat$DTAN <- scale(lmmdat$DTAN)
# lmmdat$DTN_byPhase <- scale(lmmdat$DTN_byPhase)
# lmmdat$DTN <- scale(lmmdat$DTN)

stlmm <- lmmdat[is.na(count_test_sequence),]
stlmm$st_corr <- 0
stlmm[type == "prototype" & response == "left", st_corr := 1]
stlmm[type != "prototype" & response == "right", st_corr := 1]

tdlmm <- lmmdat[!(is.na(count_test_sequence)),]

tdlmm$rt_resp <- 0
tdlmm[response == "left",rt_resp := 1]
tdlmm[response == "right",rt_resp := 0]
tdlmm[response == "down",rt_resp := NA]
tdlmm[response == "None",rt_resp := NA]

t2lmm <- merge(stlmm,tdlmm,by=c("datetime","stim",
                  "workerId","type","DTF","DTAF","DTAN","DTN_byPhase","DTN"))
```

## Study phase

With these models i tried to assess which difference index explains familiar v novel distinction in study phase the best. As far as i understand, the model with the smallest AIC fits best to our data, which means that the mean difference from the corresponding familiar worked best here. The models all show, that the more different pictures are categorized with the highest efficacy.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

# 2Nd model
logmr2 <- glmer(st_corr ~ DTF + stid + (1|workerId),
               data = stlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")
# 3Rd model
logmr3 <- glmer(st_corr ~ DTAF + stid + (1|workerId),
               data = stlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")
# 4th model
logmr4 <- glmer(st_corr ~ DTAN + stid + (1|workerId),
               data = stlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")

tab_model(logmr2,logmr3,logmr4,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)
```

## Test phase

### Models #1 - without random slope term

Logistic mixed regression for the test phase. Does difference from prototypes or familiarity/novelty have an effect on correct categorization in the test phase?

These models use trial quality (familiar / novel) as a fixed and as a random effect.

rt_resp is recognition test response, 0 stands for 'old' and 1 stands for 'new'.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

logmr2 <- glmer(rt_resp ~ DTF * tq + stid + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")$DTF
plot_model(logmr2, type = "eff")$tq
plot_model(logmr2, type = "int")

logmr3 <- glmer(rt_resp ~ DTAF * tq + stid + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")$DTAF
plot_model(logmr3, type = "eff")$tq
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ DTAN * tq + stid + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")$DTAN
plot_model(logmr4, type = "eff")$tq
plot_model(logmr4, type = "int")

tab_model(logmr2,logmr3,logmr4,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)

```

### Models #2 - with random slope (trial quality)

Logistic mixed regression for the test phase. Does difference from prototypes or familiarity/novelty have an effect on correct categorization in the test phase?

These models use trial quality (familiar / novel) as a fixed effect only.

rt_resp is recognition test response, 0 stands for 'old' and 1 stands for 'new'.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

logmr2 <- glmer(rt_resp ~ DTF * tq + stid + (tq|workerId),
               data = tdlmm,
               family = binomial,
               control = lmerControl(optCtrl=list(xtol_abs=1e-8, ftol_abs=1e-8, maxeval=100000)))
summary(logmr2)
plot_model(logmr2, type = "eff")$DTF +
  scale_y_continuous(limits = c(0, 0.7), 
                     labels = scales::percent_format(accuracy = 1)) +
  ggtitle("Predicted probability of 'already seen' response") + 
  ylab("")

plot_model(logmr2, type = "eff")$tq +
  scale_y_continuous(limits = c(0.25, 0.45), 
                     labels = scales::percent_format(accuracy = 1)) +
  ggtitle("Predicted probability of 'already seen' response") + 
  ylab("") + 
  xlab("") +
  scale_x_discrete(limits=c("new" = "distractor", "old" = "previously presented"))

plot_model(logmr2, type = "int") +
  scale_y_continuous(limits = c(0, 0.7), 
                     labels = scales::percent_format(accuracy = 1)) +
  ggtitle("Predicted probability of 'already seen' response") + 
  ylab("") +
  scale_color_discrete(name = "Trial type", labels=c("new" = "distractor", "old" = "prev. pres")) 

logmr3 <- glmer(rt_resp ~ DTAF * tq + stid + (tq|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")$DTAF
plot_model(logmr3, type = "eff")$tq
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ DTAN * tq + stid + (tq|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")$DTAN
plot_model(logmr4, type = "eff")$tq
plot_model(logmr4, type = "int")

tab_model(logmr2,logmr3,logmr4,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)

```

### Models #3 - with random slope (d index)

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

logmr2 <- glmer(rt_resp ~ DTF * tq + stid + (DTF|workerId),
               data = tdlmm,
               family = binomial,
               control = lmerControl(optCtrl=list(xtol_abs=1e-8, ftol_abs=1e-8, maxeval=100000)))
summary(logmr2)
plot_model(logmr2, type = "eff")$DTF +
  scale_y_continuous(limits = c(0, 0.7), 
                     labels = scales::percent_format(accuracy = 1)) +
  ggtitle("Predicted probability of 'already seen' response") + 
  ylab("")

plot_model(logmr2, type = "eff")$tq +
  scale_y_continuous(limits = c(0.25, 0.45), 
                     labels = scales::percent_format(accuracy = 1)) +
  ggtitle("Predicted probability of 'already seen' response") + 
  ylab("") + 
  xlab("") +
  scale_x_discrete(limits=c("new" = "distractor", "old" = "previously presented"))

plot_model(logmr2, type = "int") +
  scale_y_continuous(limits = c(0, 0.7), 
                     labels = scales::percent_format(accuracy = 1)) +
  ggtitle("Predicted probability of 'already seen' response") + 
  ylab("") +
  scale_color_discrete(name = "Trial type", labels=c("new" = "distractor", "old" = "prev. pres")) 

logmr3 <- glmer(rt_resp ~ DTAF * tq + stid + (DTAF|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")$DTAF
plot_model(logmr3, type = "eff")$tq
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp ~ DTAN * tq + stid + (DTAN|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")$DTAN
plot_model(logmr4, type = "eff")$tq
plot_model(logmr4, type = "int")

tab_model(logmr2,logmr3,logmr4,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)

```