---
title: "Graded Novelty Encoding Task - pilot - RUN 2 Analysis"
output: html_document
---
# The study

### Familiarization phase
Participants see 5 stimuli repeated 8 times each. Stimuli consist of a 3x3 grid, with 5 random shapes (circle,triangle,square) placed randomly (any 9 cells) with random color (red,blue,yellow,green,orange,purple).

### Study phase
Participants see the 5 familiar stimuli 5 times each (25) and 50 novel stimuli. They have to judge if the current stimulus is one of the familiars. The novels differ to a differing degree from the familiars: there is 5x2 (two for each familiar) that is wholly different (diffarr). 5x2 that has the same placement of random shapes (sarr), 5x2 same arrangement and shapes (sarrsha), 5x2 same arrangement and colors (sarrcol) 5x2 same arrangement, shapes and colors (colors are randomized, thus, these are not the same as the familiars - sarrshacol). 

### Test phase
Participants see the novels from the study phase and 50 new stimuli (sarr - 10, sarrsha - 10, etc.). Participants have to signal if they have already seen the current stimulus or it is wholly new. They had the option to signal "maybe", but were asked to do this in moderation (maybe resp <= 20). These responses have been added to correct responses.

```{r  include=FALSE}
library(ez)
library(ggplot2)
library(emmeans)
library(DescTools)
library(stats)
library(afex)
library(effsize)
library(lubridate)
source("difference_innumbers.R")
source("datproc_2ndrun.R")
GNET_pilot_alldata <- GNET_pilot_RUN2_alldata
rm(GNET_pilot_RUN2_alldata)

# EXCLUSIONs ####

# extract the number of all separate runs - allruns
allruns <- unique(GNET_pilot_alldata[,c("studyResultId","workerId")])
allruns <- na.omit(allruns)
allruns <- nrow(allruns)

# REMOVE INSUFFICIENT DATA
ids <- GNET_pilot_alldata[, .(rowCount = .N), by = c("workerId","studyResultId","datetime")]
ids[,RUNIDENTIFIER := paste(ids$workerId, "_", ids$studyResultId, sep="")]
ids <- ids[rowCount >= 175]
GNET_pilot_alldata <-
  GNET_pilot_alldata[workerId %in% ids$workerId & studyResultId %in% ids$studyResultId,]
GNET_pilot_alldata <- 
  GNET_pilot_alldata[!duplicated(GNET_pilot_alldata),]
completeruns <- nrow(ids)

# REMOVE TOO MUCH MISSED RESPONSES
ResponsesSummary <- GNET_pilot_alldata[, .(rowCount = .N), by = .(workerId,studyResultId,type,tq,response)]
MissedResSummary <- ResponsesSummary[response == "None", sum(rowCount),by = .(workerId,studyResultId)]
MissedResSummary <- MissedResSummary[V1 < 66,]
GNET_pilot_alldata <-
  GNET_pilot_alldata[(workerId %in% MissedResSummary$workerId) & (studyResultId %in% MissedResSummary$studyResultId),]
# Nr of exclusions due to misses
ExcludeMisses <- nrow(ids) - nrow(MissedResSummary)

# túl alacsony prototype recog rate a study alatt kipottyan
StudySummary <- GNET_pilot_alldata[is.na(count_test_sequence) & response == "left" & type == "prototype", .N/25, by=.(workerId,studyResultId)]
StudySummary <- StudySummary[V1 > 0.5]
ExcludePrototypeRecog <- nrow(MissedResSummary) - nrow(StudySummary)
GNET_pilot_alldata <-
  GNET_pilot_alldata[(workerId %in% StudySummary$workerId) & (studyResultId %in% MissedResSummary$studyResultId),]

# túl sok maybe response kipottyan
TestSummary <- GNET_pilot_alldata[!is.na(count_test_sequence) & response == "down", .N, by=.(workerId,studyResultId)]
TestSummary <- TestSummary[N < 25]
ExcludeMaybeResp <- nrow(StudySummary) - nrow(TestSummary)
GNET_pilot_alldata <-
  GNET_pilot_alldata[(workerId %in% TestSummary$workerId) & (studyResultId %in% MissedResSummary$studyResultId),]

GNET_pilot_filtered <- GNET_pilot_alldata

rm(GNET_pilot_alldata,ids,MissedResSummary,ResponsesSummary,StudySummary)
#### exclude those cases where a participant completed multiple runs (only first is kept)
multipleruns <- GNET_pilot_filtered[,sum(DTF),by=.(workerId,studyResultId,datetime)]
multipleruns$datetime <- mdy_hms(multipleruns$datetime)
mrs <- c(multipleruns$workerId[duplicated(multipleruns$workerId)])
for (i in 1:length(mrs)){
  temp <- multipleruns[workerId == mrs[i]]
  first <- min(temp$datetime)
  temp <- temp[datetime != first,]
  GNET_pilot_filtered <- GNET_pilot_filtered[!(workerId %in% temp & studyResultId %in% temp),]
}
rm(temp,first,multipleruns)
ExcludeMRuns <- length(mrs)
rm(mrs)
#####
```


## Participants

The online task has been started a total of `r allruns` times.

We excluded a total of `r allruns - completeruns` runs due to irregular data leaving `r completeruns` in the analysis.

We excluded some (`r ExcludeMisses`) runs as they missed more than 66 of 175 trials.

We also excluded `r ExcludePrototypeRecog` runs in which the participant recognized less than half of the prototypes in the study phase.

We also excluded `r ExcludeMaybeResp` participants as they overused "maybe" responses in the test phase (more than 25).

We also excluded `r ExcludeMRuns` run(s) as only the first run is kept in the analysis from one participant.

This left a total of `r nrow(GNET_pilot_filtered)/175` participants.

Maybe responses [mean(±sd)] : `r mean(TestSummary$N)` ± `r sd(TestSummary$N)`

```{r  include=FALSE}
source("registerdata_in.R")

jkwid <- jkwid[X.U.FEFF.id %in% TestSummary$workerId]
registernmail <- registernmail[X.U.FEFF.id %in% TestSummary$workerId]

jkwid <- jkwid[,c("age","gen")]
registernmail <- registernmail[,c("age","gen")]

demog <- rbind(jkwid,registernmail)
rm(jkwid,registernmail)

```

The sample had a mean(±sd) age of `r mean(demog$age)` ± `r sd(demog$age)`.

The histogram below shows the number of participants completing the task in a given hour of the day.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
exptimes <- exptimes[X.U.FEFF.id %in% TestSummary$workerId]

ggplot(exptimes,aes(hour)) +
  geom_histogram(color="black",fill="lightblue") +
  ggtitle("The hour of the day when participants completed the task") +
  ylab("Nr of participants") +
  xlab("Hour of the day")
```

```{r  include=FALSE}
source("means_2ndrun.R")
```

## Study phase:

During the study phase, the participants see familiar and novel items.

The participants produced a mean (±sd) recognition rate of `r mean(Study_ResponsesByType$N[Study_ResponsesByType$type == "prototype" & Study_ResponsesByType$response == "left"])/25` ± `r sd(Study_ResponsesByType$N[Study_ResponsesByType$type == "prototype" & Study_ResponsesByType$response == "left"])/25` for familiar pictures.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
test <- t.test(Study_ResponsesByType$N[Study_ResponsesByType$type == "prototype" & Study_ResponsesByType$response == "left"]/25,
               mu = 0.5,
               alternative = "two.sided")
cohend <- cohen.d(Study_ResponsesByType$N[Study_ResponsesByType$type == "prototype" & Study_ResponsesByType$response == "left"]/25,NA,
                  paired = FALSE,conf.level=0.95, mu = 0.5)

```

The sample performed above chance levels, as a one sample t-test showed (t(`r test$parameter[[1]]`)=`r test$statistic[[1]]`, p = `r test$p.value`, Cohen's d = `r cohend$estimate`, 95% CI:`r cohend$conf.int[[1]]` - `r cohend$conf.int[[2]]`).

We use an ANOVA to see if there is a difference in correct rejection for the different novels.
```{r  eval = TRUE, warning=FALSE, echo=FALSE}
# ezANOVA(study_dat_news, dv =  crrate, within = type, wid = workerId)
a1 <- aov_ez("workerId", "N",
             Study_CorrRejectionByType, within = "type")
a1
m3 <- emmeans(a1, ~ type)
pairs(m3)
contrast(m3, "poly")
ggplot(Study_CorrRejectionByType, aes(x=type, y=N, color = type)) + 
  geom_jitter(width=0.2, alpha=0.2) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) + 
  ggtitle("Number of correct rejections in the study phase by novel picture category") +
  xlab("") +
  ylab("Nr of correct rejections") +
  theme(legend.position = "none")
```

## Test phase:

This phase tests the learning that has occurred during the study phase. If the participants learned the novels in the study phase, their responses should differ for the stimuli that they have already seen during the study phase (familiars) and those that they see for the first time during the test phase (novels). We also let the participants to choose "maybe" by pressing the down arrow, but asked them not to overuse this response (maybe resp <= 50). We added these responses as correct responses to both stimulus categories.

```{r  warning=FALSE, echo=FALSE}

print("A t-test to compare the number of old responses btwn old and new stim")
# print(t.test(test_dat_c_tq$V1[test_dat_c_tq$rkey == "left" & test_dat_c_tq$tq == "fam"],test_dat_c_tq$V1[test_dat_c_tq$rkey == "left" & test_dat_c_tq$tq == "new"], paired=TRUE))

a <- Test_ResponsesByType$recog_O
b <- Test_ResponsesByType$fa_N
ttest2 <- t.test(a,b,paired = TRUE)
cd2 <- cohen.d(a,b,paired = TRUE,conf.level=0.95)
d <- with(Test_ResponsesByType, recog_O - fa_N)
st2 <- shapiro.test(d)

dlong <- melt(Test_ResponsesByType[,c("workerId", "type", "recog_O", "fa_N")], id.vars=c("workerId", "type"))  

#"value" and "variable" are default output column names of melt()
ggplot(dlong, aes(variable,value, color=type)) +
  stat_summary(geom = "point",fun.y = "mean",size = 2,shape = 16,position=position_dodge(width=0.4)) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.2,position=position_dodge(width=0.4)) +
  stat_summary(fun.y=mean, geom="text", show.legend = FALSE, 
               vjust=0.0,hjust=1.5, position=position_dodge(width=0.4),aes( label=round(..y.., digits=3))) +
  #geom_jitter(width=0.2, alpha=0.2) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", col ="black", width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col="black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=0.0,hjust=-1, aes( label=round(..y.., digits=3))) +
  scale_color_discrete(name = "Stim category", labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors","sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill"))

rm(dlong)
```

Results of the paired t-test: (t(`r ttest2$parameter[[1]]`)=`r ttest2$statistic[[1]]`, p = `r ttest2$p.value`, Cohen's d = `r cd2$estimate`, 95% CI:`r cd2$conf.int[[1]]` - `r cd2$conf.int[[2]]`).

Shapiro-Wilk is significant (p = `r st2$p.value`).

```{r  warning=FALSE, echo=FALSE}
a1 <- aov_ez("workerId", "CorrRecog",
             Test_ResponsesByType, within = c("type"))
a1
m3 <- emmeans(a1, ~ type)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(Test_ResponsesByType, aes(x=type, y=CorrRecog, color=type))+
  geom_jitter(width=0.3, alpha=0.3) +
  stat_summary(geom = "errorbar", fun.data = mean_se, col = "black", width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  ggtitle("Corrected Recognitions (Recog - FA) in the Test Phase by Picture Category")


ndf <- a1$anova_table$`num Df`
ddf <- a1$anova_table$`den Df`
p <- a1$anova_table$`Pr(>F)`
```

ANOVA (factor: TYPE (5 levels)): (F[`r ndf`,`r ddf`] = `r a1$anova_table$F`, p = `r p`, n2G = `r a1$anova_table$ges`).

```{r  warning=FALSE, echo=FALSE}
print("ANOVA with correct rejection minus false alarm by category")
a1 <- aov_ez("workerId", "CorrRejec",
             Test_ResponsesByType, within = c("type"))
a1
m3 <- emmeans(a1, ~ type)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(Test_ResponsesByType, aes(x=type, y=CorrRejec, color=type))+
  geom_jitter(width=0.3, alpha=0.3) +
  stat_summary(geom = "errorbar", fun.data = mean_se, col = "black", width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  ggtitle("Corrected Rejections (Rejec - Miss) in the Test Phase by Picture Category")

ndf <- a1$anova_table$`num Df`
ddf <- a1$anova_table$`den Df`
p <- a1$anova_table$`Pr(>F)`
```

ANOVA (factor: TYPE (5 levels)): (F[`r ndf`,`r ddf`] = `r a1$anova_table$F`, p = `r p`, n2G = `r a1$anova_table$ges`).

```{r  warning=FALSE, echo=FALSE}
print("ANOVA with Overall Corrected Categorizations ((Recog-FA)+(Reject-Miss))")
a1 <- aov_ez("workerId", "OverallCCat",
             Test_ResponsesByType, within = c("type"))
a1
m3 <- emmeans(a1, ~ type)
pairs(m3)
posthoc <- pairs(m3)
contrast(m3, "poly")

ggplot(Test_ResponsesByType, aes(x=type, y=OverallCCat, color=type))+
  geom_jitter(width=0.3, alpha=0.3) +
  stat_summary(geom = "errorbar", fun.data = mean_se, col = "black", width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  ggtitle("Corrected Rejections (Rejec - Miss) in the Test Phase by Picture Category")

ndf <- a1$anova_table$`num Df`
ddf <- a1$anova_table$`den Df`
p <- a1$anova_table$`Pr(>F)`

```

ANOVA (factor: TYPE (5 levels)): (F[`r ndf`,`r ddf`] = `r a1$anova_table$F`, p = `r p`, n2G = `r a1$anova_table$ges`).

# Mixed models

```{r  warning=FALSE, echo=FALSE}
library(lme4)
library(lmerTest)
library(sjPlot)

tdlmm <- GNET_pilot_RUN2_filtered[!is.na(count_test_sequence)]
tdlmm$rt_resp_old0 <- NA
tdlmm[response == "left",rt_resp_old0 := 0]
tdlmm[response == "right",rt_resp_old0 := 1]
tdlmm$rt_resp_old0 <- as.factor(tdlmm$rt_resp_old0)

logmr <- glmer(rt_resp_old0 ~ type * tq + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr)
plot_model(logmr, type = "eff")$type
plot_model(logmr, type = "eff")$tq
plot_model(logmr, type = "int")

logmr2 <- glmer(rt_resp_old0 ~ DTF * tq + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr2)
plot_model(logmr2, type = "eff")$DTF
plot_model(logmr2, type = "eff")$tq
plot_model(logmr2, type = "int")

logmr3 <- glmer(rt_resp_old0 ~ DTAF * tq + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr3)
plot_model(logmr3, type = "eff")$DTAF
plot_model(logmr3, type = "eff")$tq
plot_model(logmr3, type = "int")

logmr4 <- glmer(rt_resp_old0 ~ DTAN * tq + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr4)
plot_model(logmr4, type = "eff")$DTAN
plot_model(logmr4, type = "eff")$tq
plot_model(logmr4, type = "int")

logmr5 <- glmer(rt_resp_old0 ~ DTN_byPhase * tq + (1|workerId),
               data = tdlmm,
               family = binomial)
summary(logmr5)
plot_model(logmr5, type = "eff")$DTN_byPhase
plot_model(logmr5, type = "eff")$tq
plot_model(logmr5, type = "int")

# logmr6 <- glmer(rt_resp ~ DTPPm * tq + (1|workerId),
#                data = tdlmm,
#                family = binomial)
# summary(logmr6)
# plot_model(logmr6, type = "eff")$DTPPm
# plot_model(logmr6, type = "eff")$tq
# plot_model(logmr6, type = "int")

tab_model(logmr, logmr2,logmr3,logmr4,logmr5,# logmr6,
          # = c("Model 1", "Model 2", "Model 3", "Model 4"),
          show.est = TRUE,
          # show.ci = TRUE,
          show.se = TRUE,
          show.r2 = TRUE,
          # show.adj.icc = TRUE,
          # show.icc = FALSE,
          # pred.labels =
          show.aic = TRUE,
          show.aicc = TRUE,
          # show.std = TRUE,
          transform = NULL)

```