---
title: "Graded Novelty Enoding Task - Stimulus pool analysis"
output: html_document
---
```{r  include=FALSE}
source("difference_innumbers.R")

library(ez)
library(ggplot2)
library(emmeans)
library(DescTools)
library(stats)
library(afex)
library(effsize)
```

# The metrics

### Differences between the prototypes

```{r  eval = TRUE, warning=FALSE, echo=FALSE}

differences <- c()
for (i in 1:nrow(prot_arr)){
  comp_p_arr <- prot_arr[pict != prot_arr$pict[i]]
  comp_p_col <- prot_col[pict != prot_col$pict[i]]
  comp_p_sha <- prot_sha[pict != prot_sha$pict[i]]
  for (j in 1:nrow(comp_p_arr)){
    arrdiff <- prot_arr[i] - comp_p_arr[j]
    ad <- table(arrdiff[,arrdiff != 0])["TRUE"][[1]]
    if (is.na(ad)){ad <- 0}
    ###
    coldiff <- prot_col[i] - comp_p_col[j]
    cd <- table(coldiff[,coldiff != 0])["TRUE"][[1]]
    if (is.na(cd)){cd <- 0}
    ###
    shadiff <- prot_sha[i] - comp_p_sha[j]
    sd <- table(shadiff[,shadiff != 0])["TRUE"][[1]]
    if (is.na(sd)){sd <- 0}
    ###
    diffsum <- ad + cd + sd
    differences <- c(differences,diffsum)
  }
}

print(mean(differences))

```

### Difference from corresponding familiar picture
All pictures are compared to a familiar. The number of differences between the three vectors of the pictures yields a difference score.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
ggplot(difftoprot, aes(x=type, y=DTF, color=type))+
  geom_jitter(width=0.2, alpha=0.8) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  theme(legend.position = "none") +
  ylab("Difference")


```



### Mean difference from all prototypes
We calculate the difference from all prototypes and take the mean for each picture in the set.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
ggplot(difftoprots[type != "",], aes(x=type, y=DTAF, color=type))+
  geom_jitter(width=0.2, alpha=0.8) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  theme(legend.position = "none") + 
  ylab("Difference")
```

### Mean difference from all other pictures in the same category
We calculate the differences between each pair of pictures and then take the mean of these differences (19 comparisons per stim).

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
ggplot(diffinnovs[type != "",], aes(x=type, y=DTAN, color=type))+
  geom_jitter(width=0.2, alpha=0.8) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  theme(legend.position = "none") + 
  ylab("Difference")
```

### Mean difference from all other pictures in the same category per study/test phase
We calculate the differences between each pair of pictures and then take the mean of these differences (9 comparisons per stim).

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
ggplot(diffinnovs2[type != "",], aes(x=type, y=DTN_byPhase, color=type))+
  geom_jitter(width=0.2, alpha=0.8) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.2) +
  stat_summary(geom = "point",fun.y = "mean",col = "black",size = 2,shape = 16) +
  stat_summary(fun.y=mean, colour="black", geom="text", show.legend = FALSE, 
               vjust=-3.0, aes( label=round(..y.., digits=3))) +
  scale_x_discrete(labels=c("diffarr" = "novel layout", "sarr" = "novel shapes & colors",
                              "sarrcol" = "novel shapes", "sarrsha" = "novel colors", "sarrshacol" = "novel fill")) +
  theme(legend.position = "none") + 
  ylab("Difference") + 
  facet_wrap(~phase)
```

### DTPPm - mean Diff To Previously seen Pictures
We compare the current picture to all previously seen pictures (25 in first study trial, 26 in 2nd, and so on ..). We take the mean.

```{r  eval = TRUE, warning=FALSE, echo=FALSE}
library(ggforce)

lmmdat <- as.data.table(read.csv("filtereddata_pilot1_alldiffind.csv"))
for (i in 1:15){
  print(ggplot(lmmdat, aes(x=stimpresseq, y=DTPPm))+
    geom_jitter(aes(color=type),width=0.2, alpha=0.7) +
      geom_line(aes(x=stimpresseq, y =DTPPm), alpha=0.3) +
    ylab("Difference") + 
    facet_wrap_paginate(~ workerId, ncol = 2, nrow = 2, page = i))
}
```